Quantile regression

### 2025-02-17 landscapemetrics_quantile.Rmd
update analysis

wfs_pca_all <- prcomp(wfs_grp %>%
                        select(ntr_pland, ann_agr_pland, prn_agr_pland, 
                               aglu_iji, aglu_frac_mn),
                      scale. = TRUE, center = TRUE)

@@

wfs_mod_pca <- prcomp(wfs_grp %>% select(ntr_pland, ann_agr_pland, prn_agr_pland, 
                                         aglu_iji, aglu_frac_mn),
                      scale. = TRUE, center = TRUE)

autoplot(wfs_pca_all, data = wfs_grp, color = "habcat", 
         loadings = TRUE,
         loadings.label.label,
         choices = c(2,3))

@@

>>>>

wfs_pca_all <- prcomp(wfs_grp %>%
                        select(ntr_pland, ann_agr_pland, prn_agr_pland, 
                               aglu_iji, aglu_frac_mn, lu_shdi),
                      scale. = TRUE, center = TRUE)

@@

@@

```{r grp_pca_smp2}

wfs_pca_all2 <- prcomp(wfs_grp %>%
                        select(ntr_pland, ann_agr_pland, prn_agr_pland, 
                               aglu_iji, aglu_frac_mn),
                      scale. = TRUE, center = TRUE)

summary(wfs_pca_all2)

```{r grp_pca_mod2}

ggbiplot::ggbiplot(wfs_pca_all2, groups = wfs_grp$habcat)
ggbiplot::ggbiplot(wfs_pca_all2, groups = wfs_grp$habcat, choices = c(2,3))

```{r create_pc_var}

lsm_pc <- wfs_grp %>% cbind(predict(wfs_pca_all))

ggplot(lsm_pc, aes(PC1, pollinators_base, colour = habcat)) + geom_point()

ggplot(lsm_pc, aes(PC3, sed_export_base, colour = habcat)) + geom_point()
